---
title: "Clustering"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
params:
    scrna: 'scrna object'
    cluster: "clusters to analyse"
    cluster_info: "cluster info"
    project: "name/tag of the project"
    savedir: "directory where rds files were saved"
    funcs: "analysis steps to be performed"
    report_data_folder: "folder with the output tables"
    report_tables_folder: "folder with the table elements"
    report_plots_folder: "folder with the plot elements"
    report_plots_folder_png: "folder with the png plot elements"
    report_plots_folder_pdf: "folder with the pdf plot elements"
    author: "author of document"
author: '`r params$author`'
---

```{r , include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, echo = F,cache=F)
```

```{r echo=FALSE, include=FALSE}
library(dplyr)
library(kableExtra)
```

## Cluster: `r colorize(params$cluster_info,"red")`

### Clusters
```{r umap_groupby_name, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("umap_groupby_name_",params$cluster,".png")
  )
)
```
```{r umap_groupby_stage, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("umap_groupby_stage_",params$cluster,".png")
  )
)
```
```{r umap_groupby_cluster, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("umap_groupby_cluster_",params$cluster,".png")
  )
)
```
```{r stSample_stCond_table_cluster, echo=FALSE}
load_object(
  file.path(
    params$report_tables_folder,
    paste0("stSample_table_cluster_",params$cluster,".RDS")
  )
) %>%
  kable(caption = "samples: cluster cells", align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

load_object(
  file.path(
    params$report_tables_folder,
    paste0("stCond_table_cluster_",params$cluster,".RDS")
  )
) %>%
  kable(caption = "condition: cluster cells", align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Clusters Statistics
```{r cluster_statistics, out.width="100%", echo=FALSE, eval=(params$cluster!="singleton")}
flist = grep(
  glue("cluster_statistics_.*{params$cluster}"),
  list.files(
    params$report_plots_folder_png,
    full.names=TRUE
  ),
  perl=TRUE,
  value=TRUE
)
flist = grep(params$cluster, flist, value=TRUE, fixed=TRUE)
knitr::include_graphics(flist)
```

### Clusters proportion test
reference: https://github.com/rpolicastro/scProportionTest
```{r cluster_proptest, out.width="100%", echo=FALSE, eval=(params$cluster!="singleton")}
flist = grep(
  glue("cluster_proptest_.*{params$cluster}"),
  list.files(
    params$report_plots_folder_png,
    full.names=TRUE
  ),
  perl=TRUE,
  value=TRUE
)
flist = grep(params$cluster, flist, value=TRUE, fixed=TRUE)
knitr::include_graphics(flist)
```



### Sample proportion per cluster
```{r cluster_sample_proportions, out.width="100%", echo=FALSE, eval=(params$cluster!="singleton")}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("cluster_sample_proportions_",params$cluster,".png")
  )
)
```

### Number of cells, per cluster, per sample
```{r cluster_sample_distribution, out.width="100%", echo=FALSE, eval=(params$cluster!="singleton")}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("cluster_sample_distribution_",params$cluster,".png")
  )
)
```

### Cell cycle phase
```{r umap_ccycle_phase, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("umap_ccycle_phase_",params$cluster,".png")
  )
)
```

### QC Feature plots
```{r umap_featureplot_qc, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("umap_featureplot_qc_",params$cluster,".png")
  )
)
```
```{r umap_featureplot_ccycle, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("umap_featureplot_ccycle_",params$cluster,".png")
  )
)
```

### Doublets score
reference: https://github.com/chris-mcginnis-ucsf/DoubletFinder
```{r umap_featureplot_doublets, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("umap_featureplot_doublets_",params$cluster,".png")
  )
)
```


### QC Violin plot
```{r vlnplot_qc_ccycle_groupby, out.width="100%", echo=FALSE}
knitr::include_graphics(
  file.path(
    params$report_plots_folder_png,
    paste0("vlnplot_qc_ccycle_groupby-cluster_",params$cluster,".png")
  )
)
```

### MCA (Mouse Cell Atlas) annotation
reference: http://bis.zju.edu.cn/MCA/
```{r mca_annotate, out.width="100%", echo=FALSE, eval=(params$cluster!="singleton")}
fname <- file.path(
    params$report_plots_folder_png,
    paste0("mca_annotate_",params$cluster,".png")
  )
if(file.exists(fname)) knitr::include_graphics(fname)
```
```{r mca_annotate_hover, out.width="100%", echo=FALSE, eval=(FALSE & params$cluster!="singleton")}
plt = load_object(
  file.path(
    params$report_plots_folder,
    paste0("mca_annotate_plt_",params$cluster,".RDS")
  )
)
info = load_object(
  file.path(
    params$report_plots_folder,
    paste0("mca_annotate_info_",params$cluster,".RDS")
  )
)
Seurat::HoverLocator(plot = plt, information = info)
```

### HCL (Human Cell Landscape) annotation
reference: https://db.cngb.org/HCL/
```{r hcl_annotate, out.width="100%", echo=FALSE, eval=(params$cluster!="singleton")}
fname <- file.path(
    params$report_plots_folder_png,
    paste0("hcl_annotate_",params$cluster,".png")
  )
if(file.exists(fname)) knitr::include_graphics(fname)
```
```{r hcl_annotate_hover, out.width="100%", echo=FALSE, eval=(FALSE & params$cluster!="singleton")}
plt = load_object(
  file.path(
    params$report_plots_folder,
    paste0("hcl_annotate_plt_",params$cluster,".RDS")
  )
)
info = load_object(
  file.path(
    params$report_plots_folder,
    paste0("hcl_annotate_info_",params$cluster,".RDS")
  )
)
Seurat::HoverLocator(plot = plt, information = info)
```

### External Annotation
```{r external_annotation, out.width="100%", echo=FALSE, eval=(params$cluster!="singleton")}
fname <- file.path(
    params$report_plots_folder_png,
    paste0("external_annotation_",params$cluster,".png")
  )
if(file.exists(fname)) knitr::include_graphics(fname)
```
```{r external_annotation_hover, out.width="100%", echo=FALSE, eval=(FALSE & params$cluster!="singleton")}
plt = load_object(
  file.path(
    params$report_plots_folder,
    paste0("external_annotation_plt_",params$cluster,".RDS")
  )
)
info = load_object(
  file.path(
    params$report_plots_folder,
    paste0("external_annotation_info_",params$cluster,".RDS")
  )
)
Seurat::HoverLocator(plot = plt, information = info)
```
